---
title: "Resume"
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    # set it to true for a self-contained HTML page but it'll take longer to render
    self_contained: false
# uncomment this line to produce HTML and PDF in RStudio:
knit: pagedown::chrome_print
params:
  cv_name: "Javier Elio"
  data_path: "cv_data.xlsx"
---

```{r, setup, include=FALSE}
knitr::opts_chunk$set(
  results = 'asis', 
  echo = FALSE,
  message = FALSE
)

library(tidyverse)
library(readxl)
source("cv_printing_functions.r")

# Read data (from csv)
data_path <- params$data_path
cv <- create_cv_object(data_path)
cv_name <- params$cv_name
  
```

```{css}

.skill-bar {
  color: white;
  padding: 0.1rem 0.25rem;
  margin-top: 3px;
  position: relative;
  width: 100%;
}

```

Aside
================================================================================

Contact Info {#contact}
--------------------------------------------------------------------------------

```{r contact_info}

cv %>% print_contact_info()

```

Software {#software}
--------------------------------------------------------------------------------

```{r software}

cv %>% print_skill_bars()

```

Languages {#languages}
--------------------------------------------------------------------------------

```{r languages}

cv %>% print_languages()

```

Main
================================================================================

`r cv_name` {#title}
--------------------------------------------------------------------------------

I am an engineer with 10+ years of research and teaching experience, with a solid background in statistics, spatial data analysis, and modelling. My main research area is environmental science, with a particular interest in natural hazards and climate change.


Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r education}

cv %>% print_section("education")

```

Employment {data-icon=suitcase}
--------------------------------------------------------------------------------

```{r employment}

cv %>% print_section("employment")

```

Teaching Experience {data-icon=chalkboard-teacher}
--------------------------------------------------------------------------------

```{r teaching}

cv %>% print_section("teaching")

```


Selected Publications {data-icon=file}
--------------------------------------------------------------------------------

```{r publications}

cv %>% print_publications()

```

Disclaimer {#disclaimer style="width: var(--sidebar-width); padding-left: var(--sidebar-horizontal-padding);"}
--------------------------------------------------------------------------------

This resume was made with the R package [**pagedown**](https://github.com/rstudio/pagedown).

Last updated on `r Sys.Date()`.
