---
output: 
  vitae::awesomecv

date: "`r format(Sys.time(), '%B, %Y')`"

params:
  cv_name: NULL 
  cv_surname: NULL
  key_1: NULL
  key_2: NULL
  key_3: NULL
  address: NULL
  phone: NULL
  email: NULL
  website: NULL
  github: NULL
  linkedin: NULL
  twitter: NULL
  company: NULL
  company_address: NULL
  company_city: NULL
  company_position: NULL
  company_responsable: NULL
  text1: NULL
  text2: NULL
  
name: "`r params$cv_name`" 
surname: "`r params$cv_surname`"
position: "`r params$key_1` | `r params$key_2` | `r params$key_3`"
address: "`r params$address`"
phone: "`r params$phone`"
email: "`r params$email`"
website: "`r params$website`"
github: "`r params$github`"
linkedin: "`r params$linkedin`"
twitter: "`r params$twitter`"

header-includes:
  - \usepackage{colortbl}
  - \definecolor{darktext}{HTML}{414141}
  - \definecolor{text}{HTML}{333333}
  - \definecolor{graytext}{HTML}{5D5D5D}
  - \definecolor{lighttext}{HTML}{999999}
---

```{r setup, include = FALSE}
# - \photo[circle, noedge, left]{photo.png}

knitr::opts_chunk$set(
  results = 'asis', 
  echo = FALSE,
  message = FALSE, 
  warning = FALSE)

library(vitae)
library(knitr)
library(kableExtra)
library(vitae)
```

\vspace{1.25cm} \rightline{\textcolor{graytext}{\today}}

\vspace{-0.5cm}  **`r params$company`**    \
\textcolor{graytext}{`r params$company_address`}     \
\textcolor{graytext}{`r params$company_city`}             

\vspace{0.25cm}\textbf{\underline{`r params$company_position`}}  
\vspace{0.15cm} \textcolor{graytext}{`r paste0("Dear " , params$company_responsable, ",")`}

```{r text-block-1}
cat("\\vspace{0.5cm}\n# About me\n")
```

`r params$text1`

```{r text-block-2}
cat("\\vspace{0.5cm}\n# Personal vision of the position\n")
``` 

`r params$text2`


\vspace*{0.5cm}
Sincerely,

\vspace*{0.5cm}
\textbf{`r paste(params$cv_name, params$cv_surname)`}

\vspace*{0.5cm} Attached: Curriculum Vitae

