---
output: vitae::awesomecv
params:
  cv_name: Javier 
  cv_surname: Elio
  data_path: "cv_data.xlsx"
  key_1: Researcher
  key_2: Environemntal sciences
  key_3: Geoinformatics
  address: Haugesund (Norway)
  phone: +47 4125 91 17
  email: javiereliomedina@gmail.com
  website: https://javierelio.netlify.app/
  github: javiereliomedina
  linkedin: javiereliomedina
  twitter: Elio_Javi 
  
name: "`r params$cv_name`" 
surname: "`r params$cv_surname`"
date: "`r format(Sys.time(), '%B, %Y')`"
position: "`r params$key_1` | `r params$key_2` | `r params$key_3`"
address: "`r params$address`"
phone: "`r params$phone`"
email: "`r params$email`"
website: "`r params$website`"
github: "`r params$github`"
linkedin: "`r params$linkedin`"
twitter: "`r params$twitter`"
header-includes:
  - \usepackage{colortbl}
  - \usepackage{longtable}
  - \usepackage{float}
  - \arrayrulecolor{white}
  - \definecolor{darktext}{HTML}{414141}
  - \definecolor{blue}{rgb}{0.0, 0.0, 1.0}
---

```{r setup, include = FALSE}

knitr::opts_chunk$set(
  results = 'asis', 
  echo = FALSE,
  message = FALSE, 
  warning = FALSE
)

library(tidyverse)
library(readxl)
library(knitr)
library(kableExtra)

source("cv_long_printing_functions.r")

# Read data (from csv)
data_path <- params$data_path
cv <- create_cv_object(data_path)
cv_name <- params$cv_name
cv_surname <- params$cv_surname

# # Print sections if TRUE
# eval_text <- params$summary
# eval_sof  <- params$software
# eval_lan  <- params$languages
# eval_edu  <- params$education
# eval_emp  <- params$employment
# eval_tea  <- params$teaching
# eval_pub  <- params$publications
# eval_pck  <- params$packages
# eval_app  <- params$apps

# Short sentence with expertise
research_text <- "My research interests are:"
  
```

\vspace{0.5cm}
\footnotesize 
\rightline{\textcolor{darktext}{\textit{`r pull(filter(cv$text_blocks, loc == "short_description"), text)`}}}
\normalsize

\vspace{0.5cm}

# Career Summary

\vspace{-0.1cm}

```{r text-block-1}

cv %>% print_text_block("intro")

```

```{r text-block-2}

cat("My research interests are:")
  
```

```{r text-block-3}

cv %>% print_reserch_intrerest()

```

# Education

\vspace{-0.1cm}

```{r education}

cv %>% print_section("education")

```

\vspace{-1cm}

# Experience

\vspace{-0.1cm}

```{r experience}

cv %>% print_section("employment")
  
```

\vspace{-1cm}

# Invited positions

\vspace{-0.1cm}

```{r inv_positions}

cv %>% print_section("inv_position")
  
```

\vspace{-1cm}

# Professional memberships

\vspace{-0.1cm}

```{r memberships}

cv %>% print_section("membership")
  
```

\vspace{-1cm}

# Professional services

\vspace{-0.1cm}

```{r Services}

cv %>% print_section("service")
  
```

\vspace{-1cm}

# Funding projects

\vspace{-0.1cm}

```{r funding}
  
cv %>% print_section("project")

```

\vspace{-1cm}

# Honours and awards

\vspace{-0.1cm}

```{r awards}
  
cv %>% print_section("award")

```

\vspace{-1cm}

# Training and teaching experience

## Lectures/Seminars

\vspace{-0.1cm}

```{r lectures}

cv %>% print_section("teaching")

```

\vspace{-1cm}

## Supervision

\vspace{-0.1cm}

```{r supervision}

cv %>% print_section("supervision")

```

\vspace{-1cm}

## External sensor

\vspace{-0.1cm}

```{r ext-sensor}

cv %>% print_section("ext_sensor")

```

\vspace{-1cm}

# Publications

\vspace{-0.1cm}

I have published **`r length(cv$publications$title)`** peer-reviewed journal articles, chapters or books on Environmental Science topics. I have also presented my research at 4 invited talks, and in several national and international conferences.

## Peer reviewed articles

\vspace{-0.1cm}

```{r articles}

  cv %>% print_publications("article", cv_surname)

```

\vspace{-0.5cm}

## Books and book chapters

\vspace{-0.1cm}

```{r books}

   cv %>% print_publications("book", cv_surname)

```

